\chapter{Requirement Analysis}
\section{User Side Requirements}
\begin{enumerate}
 \item User should have an android mobile device running OS version 2.1 or above.
 \item User should have Android Application installed within the mobile.
 \item User must be able to connect the device using USB cable
 \item User must be able to connect device using Wi-Fi.
 \item User must have internet plan enabled on his device or use Wi-Fi connection for
online synchronization.
 \item Interface must be user friendly and attractive.
\end{enumerate}

\section{System Side Requirements}
\begin{enumerate}
 \item System must have Android based drivers for USB and Wi-Fi adapters.
 \item The server side application must be installed on the standard PC.
 \item System must be connected to the internet for online synchronization.
 \item Interface must be user friendly and attractive.
\end{enumerate}

\section{Hardware and Software Requirements}
\begin{enumerate}
 \item Android Based Mobile with minimum of:
 \begin{enumerate}[a. ]
  \item 128KB non-volatile memory to run Mobile Information Device (MID).
  \item 8KB of non-volatile memory for storage of persistent application data.
  \item 2KB of volatile memory to run JVM
 \end{enumerate}
 \item Device should have Wi-Fi connectivity.
 \item 600mhz processor
 \item 150 MB of RAM
\end{enumerate}

\section{Non-functional Requirement}
\subsection{Security Requirements}
\hspace*{0.82cm}In our product, security is of out-most importance. Hence we need to implement
communication over HTTPS. For that it is required that the user should be in an environment where
the HTTPS port is not blocked. In case these ports are not enabled, an http connection will have to be
used. This means using http instead of https would lead to vulnerability of the user’s data to be sniffed
by third-party. Hence this should be considered as a security requirement of the product.

\subsection{Performance Requirements}
\subsection{Safety Requirements}
\subsection{Software Quality Attributes}
\subsection{Stockholder and User Description}

\section{External Interface Requirements}
\subsection{Hardware Interfaces}
\hspace*{0.82cm}Typical hardware interfaces that would be required would be the standard USB data cable
provided with the device. No other additional hardware interfacing would be needed to be bought by
the user. Also Bluetooth and/or Wi-Fi adapter on the server machine would be needed for
communication (in case USB cable is not available). Communication protocol would be developer
implemented and the user need not worry about communicating using this protocol. Hence this
product will be extremely user-friendly.

\subsection{Software Interfaces}
\hspace*{0.82cm}The product featured, requires a database to be maintained at both the ends - client and server.
Hence we will be deploying two different databases on both of them which will be in sync on
demand.\\[0.5cm]
\hspace*{0.82cm}The client DB will be implemented using SQLite and the server DB will be standard
PostgreSQL. The UI on client will be a typical android user interface using the default options
available at the time of development. UI on server will be implemented using Qt and python at the
backend.

\subsection{Communications Interfaces}
\hspace*{0.82cm}This product basically works on the client-server architecture. Hence a communication
mechanism between server and client has to be developed. This communication will be established
over https or local Bluetooth or Wi-Fi. USB cable is another option. E-mails can be used to
send/receive reports, log files.