%\hspace*{0.82cm}\\[0.5cm]
\chapter{Software Requirements Specification}
\section{Introduction}
\subsection{Purpose}
\hspace*{0.82cm}This project aims at developing the Synchronization Manager for Android based devices.
Since there isn't any generic Synchronization Manger for android which works on all platforms
(Linux, Mac and Windows); this would help lots of people who work on two or more platforms. This
Synchronization Manager would be divided into two parts as server and client. The server would
reside on PC and client would be on Android Device. Client will gather information which is to be
synchronized.
\subsection{Document Conventions}
\hspace*{0.82cm}The following are the list of conventions and acronyms used in this document and the project as well,
privileges to the software:
\begin{itemize}
 \item \textbf{Client:} Intended users for the software.
 \item \textbf{SQL:} Structured Query Language; used to retrieve information from a database
 \item \textbf{SQL Server:} A server used to store data in an organized format
 \item \textbf{IEEE:} Institute of Electrical and Electronics Engineers
 \item \textbf{Layer:} Represents a section of the project
 \item \textbf{SYNC:} Synchronization
 \item \textbf{User Interface Layer:} The section of the assignment referring to what the user interacts with directly
 \item \textbf{Application Logic Layer:} The section of the assignment referring to the Web Server. This is where all 
computations are completed
 \item \textbf{Data Storage Layer:} The section of the assignment referring to where all data is recorded
 \item \textbf{Data flow diagram:} It shows the data flow between the entities
 \item \textbf{Use Case:} A broad level diagram of the project showing a basic overview
 \item \textbf{Boolean:} A true/false notation
 \item \textbf{Interface:} Something used to communicate across different mediums
\end{itemize}

\subsection{Intended Audience}
The intended audiences for this document are:
\begin{itemize}
 \item The team members of Innovative Android Synchronization Manager.
 \item The different Android users who are the clients.
\end{itemize}

This document will be reviewed frequently by the above audiences to check if the different
phases of the project are being completed by meeting the given requirements. If there are any changes
in the requirements in the course of the project they must be included in this document by making the
necessary changes.
\subsection{Product Scope}
\hspace*{0.82cm}The primary purpose of this is to have offline synchronization. At later stages this can be
extended to have online synchronization with services such as Ubuntu One for Linux. The software
can be made available as a paid service for corporations, users who want to backup their data.
\section{Overall Description}


